WED-SQL (Draft)

### 2016-05-23 doc/paper/main_en.tex
paper: ch6

\par Advisory Locks work in a semantic level, that is, they are only useful when they have some semantic meaning in the 
application. Put in other words, the DBMS do not enforce their use and nothing is really locked. It is up to the application
to use then rightly. As an example, in the WED-server, pending WED-transitions siting in the Job\_Pool table are uniquely
identified by the attributes pair (\emph{wid},\emph{tgid}). WED-workers requests Advisory Locks based on this composite key, 
which is only granted only once for each pair until the transaction is over. When a lock is not granted for a WED-work, it
knows that some other "sibling" is currently working on that WED-transition, even tough the record is not really blocked
on the database, and then it is free to look for another task. Once again, the WED-server will blocked transactions not
holding a valid lock.

@@

\subsection{Isolamento e paralelismo}
O PostgreSQL utiliza o modelo MVCC~\cite{NAV} para manter a integridade dos dados. Isso significa que cada transação enxerga uma "foto"
do banco de dados no momento em que a mesma inicia, garantindo seu isolamento uma vez que não há compartilhamento de dados
parciais entre transações ativas. Nesse modelo de controle de concorrência, travas de leitura não conflitam com travas de escrita.

>>>>

\par Advisory Locks work on a semantic level, that is, they are only useful when they have some semantic meaning in the 
application. Put in other words, the DBMS do not enforce their use and nothing is really locked. It is up to the application
to use then rightly. As an example, in the WED-server, pending WED-transitions siting in the Job\_Pool table are uniquely
identified by the attributes pair (\emph{wid},\emph{tgid}). WED-workers requests Advisory Locks based on this composite key, 
which is only granted only once for each pair until the transaction is over. When a lock is not granted for a WED-work, it
knows that some other "sibling" is currently working on that WED-transition, even tough the record is not really blocked
on the database, and then it is free to look for another task. Once again, the WED-server will blocked transactions not
holding a valid lock.

@@

\subsection{Transaction isolation and parallelism }

PostgreSQL employs a multi version concurrency control model (MVCC) to maintain data integrity. This means that each transaction
sees a snapshot of the database taken right before it begins to run, which keeps then isolated from each other since no uncommitted 
data is shared between concurrent transactions. Another property of this model is that data read locks never conflicts with
data write locks, minimizing lock contention.
